---
title: "Homework2"
author: "Xing Yang"
date: "2017/9/20"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Question 1

```{r}
data = USArrests
a = 1.5*sd(data$Assault)
b = mean(data$Assault)
data$Assault[which((abs(data$Assault-b)/a) >= 1)]
row.names(data[which((abs(data$Assault-b)/a) >= 1), ])
```

As we can see,  four states are outliers that are Florida, Maryland, North Carolina, North Dakota.

#Question 2

```{r}
library(tidyverse)
ggplot(data = data, mapping = aes(x = Murder, y = Assault)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) 
cor.test(data$Murder, data$Assault)
```

From the plot, the murder and assault have the positive relationship, and in the correlation test, the p-value is less than 0.05, which means there are some relationship. And the correlation is 0.8018733 which is close to 1, so the correlation relationship is strong. 

#Question 3

```{r}
data = read.csv("/Users/xingyang/Desktop/5030/hw2.csv",sep = ",")
data
n <- nrow(data)
library(forecast)
library(TTR)
#samplie moving average
F2017 <- ((data[n,2] + data[n-1, 2] + data[n-2, 2])/3)
F2017
SMA(data[, 2], n = 3)[11]
```

The phone use for 2017 using a simple moving average using last 3 years is 175848268.

```{r}
#weighted moving average
w <- c(4, 1, 1)
last3 <- data[n:(n-2), 2]
sw <- w*last3
F20171 <- sum(sw)/sum(w)
F20171
#check the answer
WMA(data[,2], n = 3, wts = c(1, 1, 4))[11]
```

The phone use for 2017 using a 3-year weighted moving average is 189396150.

```{r}
#exponential smoothing
data$Ft <- 0
data$E <- 0
a <- 0.2
data$Ft[1] <- data[1,2]
for(i in 2:n){
  data$Ft[i] <- data$Ft[i-1] + a*data$E[i-1]
  data$E[i] <- data[i,2] - data$Ft[i]
}
df_es <-data
F20172 <- data$Ft[n] + a*data$E[n]
F20172
#check the answer
EMA(data[,2], wilder = T, n = 1, ratio = 0.2)[11]
```

The phone use for 2017 using exponential smoothing is 123744469.

```{r}
#linear regression trendline
library(ggplot2)
fit <- lm(data$Subscribers~data$X...Year)
print(fit)
F20173 = -3.666e+10 + (1.828e+07)*2016
F20173
```

The phone use for 2017 using linear regression trendline is 192480000.

#Question 4

```{r}
#samplie moving average
data$Ft <- 0
data$E <- 0
library(TTR)
data$Ft[2:n] <- SMA(data[, 2], n = 3)[1:n-1]
data$E[4:n] <- abs(data[4:n,2]-data$Ft[4:n])
df_sma <- data
tail(df_sma)
mean(df_sma$E[which(df_sma$E != 0)])
```

The average absolute error for simple moving average using last 3 years is 38419568.

```{r}
#weighted moving average
data$Ft <- 0
data$E <- 0
data$Ft[2:n] <- WMA(data[,2], n = 3, wts = c(1, 1, 4))[1:n-1]
data$E[4:n] = abs(data[4:n,2] - data[4:n,3])
df_wam <- data
tail(df_wam)
mean(df_wam$E[which(df_wam$E != 0)])
```

The average absolute error for 3-year weighted moving average is 29713726.

```{r}
#exponential smoothing
data$Ft <- 0
data$E <- 0
data$Ft[1] <- data[1,2]
data$Ft[2:n] <- EMA(data[,2], wilder = T, n = 1, ratio = 0.2)[1:n-1]
data$E = abs(data[,2] - data[,3])
df_ema <- data
tail(df_ema)
mean(df_ema$E[which(df_ema$E != 0)])
```

The average absolute error for exponential smoothing is 50278149.

```{r}
#linear regression trendline
data$Ft <- 0
data$E <- 0
print(fit) 
for(i in 1:n){
  data$Ft[i] <- -3.666e+10 + (1.828e+07)*data[i,1]
  data$E[i] <- abs(data[i, 2] - data$Ft[i])
}
df_lr <- data
tail(df_lr)
mean(df_lr$E)
```

The average absolute error for linear regression trendline is 11631719.

#Question 5

```{r}
mean(df_sma$E[which(df_sma$E != 0)])
mean(df_wam$E[which(df_wam$E != 0)])
mean(df_ema$E[which(df_ema$E != 0)])
mean(df_lr$E)
```

So the smallest mean absolute error is the linear regression model

#Question 6

```{r}
mean(F20171, F20172, F20173)
```

The average forecast by averaging out the three forecasts calculated in (3) is 189396150












