---
title: "Homework 1"
author: "Xing Yang"
date: "2017/9/14"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
#Question1
data = read.csv("/Users/xingyang/Desktop/5030/customertxndata.csv",sep = ",")

#Question2
nrow(data)
mean(data$Visits)
median(data$Revenue)
min(data$Transactions, na.rm = T)
max(data$Transactions, na.rm = T)
summary(data$OS)
```

The most commonly used operating system is Android.

```{r}
#Question3
ggplot(data = data, mapping = aes(x = Visits, y = Revenue)) + 
  geom_point() + 
  geom_smooth(se = F)
plot(Revenue~Visits, data = data)
```

From the plot, the correlation between the two variables is that the more visits means the higher revenue.

```{r}
#Question 4
summary(data)
```
As we can see, Transactions and Gender have missing data, I will use the mean of Transactions instead of the miss values and will delete the miss values of Gender.

```{r}
#Question 5
tran = mean(data$Transactions, na.rm = T)
data$Transactions[is.na(data$Transactions)] = tran
data1 = na.omit(data)
summary(data1)
#Question 6
data_training = data1[seq(1, nrow(data1), 2), ]
data_validation = data1[seq(2, nrow(data1), 2), ]
#Question 7
mean(data_training$Revenue)
mean(data_validation$Revenue)
```

The means are 450.1965 and 452.1243 which are almost equality, which means that the data of missing value is randomly distributed.
And the means of the orignak data is 454.9, so the method of imputing missing value used in Qustion 5 is good.

```{r}
#Question 8
library(caret)
traindata1 = createDataPartition(data1$Visits, p = .5,
                                 list = F,
                                 times = 1)
traindata = data1[traindata1, ]
summary(traindata)
testdata = data1[-traindata1,]
summary(testdata)
```







